BurgerTown Presents: Open Adcess

### 2017-04-14 paper-sponsorships.tex
economic terrorists

\subsection{Investor Science Dispute Settlement}
We have founded an Investor Science Dispute Settlement (ISDS) court to protect
businesses from results that may damage their reputation or profits.
If a research project is found to be damaging, the authors must either retract
the paper or pay a settlement equal to the estimated losses suffered by the
company.
For example, if some agitator finds that the complexity class PLS is in PPP
relative to some oracle, they will dash the hopes of the typical Sparrow Soap
consumer, leading to hygiene neglect.
Therefore, Sparrow Soap may use the IADS court to mitigate their losses from
this finding.
Moreover, since Sparrow Soap owns both of these complexity classes as defined
in section \autoref{sec:brands} their assets will lose value and
this loss must be compensated by the offending authors.
Several ``bloggers" have deigned to argue that this arrangement gives particular corporations undue influence over science and could lead to corruption. These agitators are, of course, anti-science zealots who fail to realize the emancipatory potential of this settlement system. Much as the visionary rulings of Anthony Kennedy and others have opened up our politics to make it more responsive to democratic speech, ISDS will make science more responsive to the needs of democratic actors, like 501(c)(4) ``social welfare" nonprofits. Welfare! It will democratize our understanding of reality, taking science out of the smooth, mildly scented ivory tower and cramming it into the ad-plastered public square. Science is agoraphobic but its future is in the agora of the brainscape---the marketplace of ideas---so (to coin a term) ISDS is the deagoraphobification of science. Science cannot ignore society. Science must come to where the flavor is.

What of the science that does get published? The agents who do get economically controversial results published---the humble, modest, yeoman-scientist free agents---are likely to be powerful entities in a society with concentrated private economic power, some argue. How is that democratic? Well, Madison got it right. It's not only democratic, it's the purest form of democracy: the ``mischief of the factions." Simply put, ISDS provides a powerful mechanism of checks and balances. If Hot Packets wants to get their signature snack food placed on the government's food pyramid, it would need peer-reviewed science attesting to its beneficial health effects (such as an appearance on the Doctor Conflict-of-Interest show, where the titular doctor attests to its miracle superfood status, or a research paper). To appear in print, it would have to pay off claims from competing superfoods such as Berry Loops or Jazz Flakes. The system works! But, say, if the parent companies of all products for sale wish to merge, research touting the consumer benefits and lack of monopsony would have little trouble passing ISDS.

>>>>

\subsection{Investor Science Dispute Settlement}
We have founded an Investor Science Dispute Settlement (ISDS) court to protect
businesses from results that may damage their reputation or profits.
If a research project is found to be damaging, the authors must either retract
the paper or pay a settlement equal to the estimated losses suffered by the
company.
For example, if some agitator finds that the complexity class PLS is in PPP
relative to some oracle, they will dash the hopes of the typical Sparrow Soap
consumer, leading to hygiene neglect.
Therefore, Sparrow Soap may use the IADS court to mitigate their losses from
this finding.
Moreover, since Sparrow Soap owns both of these complexity classes as defined
in section \autoref{sec:brands} their assets will lose value and
this loss must be compensated by the offending authors.

Several ``bloggers" have deigned to argue that this arrangement gives particular corporations undue influence over science and could lead to corruption. These agitators are, of course, anti-science zealots who fail to realize the emancipatory potential of this settlement system. Much as the visionary rulings of Anthony Kennedy and others have opened up our politics to make it more responsive to democratic speech, ISDS will make science more responsive to the needs of democratic actors, like 501(c)(4) ``social welfare" nonprofits. Welfare! It will democratize our understanding of reality, taking science out of the smooth, mildly scented ivory tower and cramming it into the ad-plastered public square. Science is agoraphobic but its future is in the agora of the brainscape---the marketplace of ideas---so (to coin a term) ISDS is the deagoraphobification of science. Science cannot ignore society. Science must come to where the flavor is.

What of the science that does get published? The agents who do get economically controversial results published---the humble, modest, yeoman-scientist free agents---are likely to be powerful entities in a society with concentrated private economic power, some argue. How is that democratic? Well, Madison got it right. It's not only democratic, it's the purest form of democracy: the ``mischief of the factions." Simply put, ISDS provides a powerful mechanism of checks and balances. If Hot Packets wants to get their signature snack food placed on the government's food pyramid, it would need peer-reviewed science attesting to its beneficial health effects (such as an appearance on the Doctor Conflict-of-Interest show, where the titular doctor attests to its miracle superfood status, or a research paper). To appear in print, it would have to pay off claims from competing superfoods such as Berry Loops or Jazz Flakes. The system works! But, say, if the parent companies of all products for sale wish to merge, research touting the consumer benefits and questioning Robinsonian labor market monopsony would have little trouble passing ISDS. Approved ideas get approved quickly, and the system works!

ISDS also applies to scientists in their personal lives. If a scientist, for instance, posts to social media video of an alleged bad encounter with an internet service provider's customer service representative or video of hose water burning---and ISDS tribunal statisticians (employees of the ISDS corporate community, on rotation) determine that, as a result of these actions, shareholders lost value---then the economic terrorists promulgating this ticker-tanking tripe will have to compensate all shareholders for the drop in share price, as well as the social media platform monopoly's shareholders (if applicable; scientists should not be using free, distributed social networks but may use privately held proprietary platforms) for the shame they've brought to the platform even if share price was unaffected. This way, the integrity of the scientific process is protected---and scientists represent science with honor---in all spheres, not just peer-reviewed journals.
